### 2018-04-19 paper/paper.tex
additional paper updates

However, the degree with lowest validation error was 13.  Training error for the 13th degree polynomial was 0.384.

@@

However, the number of RBF kernels with lowest validation error was 9.  Training error was 0.337.

@@

>>>>

However, the degree with lowest validation error was 13.  Test error for the 13th degree polynomial was 0.384.

@@

However, the number of RBF kernels with lowest validation error was 9.  Testing error was 0.337.

@@

We found that RBF models behaved similarly to polynomial models, but performed significantly better.  The best fit of a polynomial model, polynomial degree 13, had an test error of 0.384, while the best RBF model, 9 Kernels, had a test error of 0.337.  However, it should be noted that overfitting with higher numbers of parameters is much more severe with RBF models.
